\def\papersize{4}
\input{preamble.inc}

\begin{document}

\title{Normal Procedures Checklist D-EDGX}
\versionchecklist{0.3}
\datechecklist{12.03.2023}

\begin{checklist}{Before Start}
  \item{Preflight Inspection}{performed}
  \item{Seats}{adjusted \& locked}
  \item{Seat Belts}{fastened}
  \item{Flaps}{retracted}
  \item{Circuit Breakers}{check}
\end{checklist}

\begin{checklist}{Engine Start}
  \item{Fuel Selector Valve}{both}
  \item{Avionics}{off}
  \item{Main Switch}{on}
  \item{Strobes}{on}
  \item{Parking/Toe Brakes}{on}
  \item{Throttle}{Open 1/4 inch}
  \item{Prime}{as rqrd.}
  \item{Mixture}{full lean}
  \hint{FULL RICH WHEN ENGINE STARTS TO FIRE}
  \item{Propeller}{max. rpm}
  \item{Prop Area}{clear}
  \item{Ignition Switch}{start}
\end{checklist}

\begin{checklist}{After Start}
  \item{Oil Pressure}{green}
    \hint{IF OIL PRESSURE DOES NOT EXCEED 25 PSI}
    \hint{WITHIN 30 SECONDS, SHUT DOWN ENGINE.}
  \item{Alternator}{check charging}
  \item{Avionics}{on}
\end{checklist}

\begin{checklist}{Engine Check}
  \item{Parking/Toe Brakes}{on}
  \item{Engine Instruments}{green}
  \item{Throttle}{2000 rpm}
  \item{Magnetos}{check}
    \hint{MAX. DROP 175 RPM}
    \hint{MAX. DIFF. 50 RPM}
  \item{Propeller}{retard slowly}
    \hint{RETARD SLOWLY UNTIL A 500 RPM DROP IS NOTED}
    \hint{REPEAT TWO TIMES}
  \item{Propeller}{max. rpm}
  \item{Alternate Air}{check}
    \hint{RPM DROP APPROX. 50 RPM}
  \item{Vacuum Gauge}{green}
  \item{Throttle}{idle}
\end{checklist}

\begin{checklist}{Before Takeoff}
  \item{Attitude Indicator}{check erect}
  \item{Altimeter}{set}
  \item{Directional Indicator}{set}
  \item{Transponder}{alt}
  \item{Boost Pump}{on}
  \item{Landing Lights}{on}
  \item{Flaps}{1}
  \item{Trim}{Takeoff}
  \item{Fuel Selector}{both}
  \item{Flight Controls}{free \& proper travel}
  \item{Seat Belts}{recheck fastened}
  \item{Doors}{closed \& latched}
  \item{Propeller}{max. rpm}
  \item{Mixture}{full rich}
\end{checklist}

\begin{checklist}{After Takeoff}
  \item{Boost Pump}{off}
  \item{Landing Lights}{off}
  \item{Flaps}{retracted}
\end{checklist}

\begin{checklist}{(Right) Base}
  \item{Tow Cable}{retracted}
  \item{Walldorf Radio}{informed}
    \hint{Tow hight \& Tow cable status}
\end{checklist}

\begin{checklist}{Landing}
  \item{Seat Belts}{fastened}
  \item{Tow Cable}{retracted}
  \item{Boost Pump}{on}
  \item{Landing Lights}{on}
  \item{Propeller}{max. rpm}
  \item{Mixture}{full rich}
  \item{Flaps}{2 / as rqrd.}
    \hint{SET 0 IF >= 12 KTS CROSSWIND}
\end{checklist}

\begin{checklist}{After Landing}
  \item{Transponder}{STBY}
  \item{Boost Pump}{off}
  \item{Landing Lights}{off}
  \item{Flaps}{retracted}
\end{checklist}

\begin{checklist}{Engine Shutdown}
  \item{Avionik}{off}
  \item{Throttle}{idle}
  \item{Magneto Grounding}{Check}
    \hint{PERFORM BELOW 1000 RPM}
  \item{Mixture}{cut-off}
  \item{Ignition Switch}{off}
  \item{Strobes}{off}
  \item{Main Switch}{off}
\end{checklist}

\end{document}